openarchaeoCollaboration

### 2023-01-30 analysis/paper.qmd
Switch to quarto

---
title: "openarchaeoCollaboration"
author:
  - name: Zack Batist
    url: https://zackbatist.github.io
    affiliation: University of Toronto
  - name: Joe Roe
    url: https://joeroe.io
    affiliation: University of Copenhagen
date: "`r Sys.Date()`"
output: distill::distill_article
---

@@

| Category                              | Kind      | Scope                                                                                                                                                                                                        |
|:--------------------------------------|:----------|:-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
| Packages and libraries                | Software  | Sets of functions assembled with clear purpose, and made accessible using standards established by an underlying platform.                                                                                   |
| Standalone software                   | Software  | Software that may be operated without needing to first access an underlying platform.                                                                                                                        |
| Scripts                               | Software  | Sets of pragmatically assembled mutable functions, often lacking complete documentation or adherence to protocols that would otherwise facilitate secondary use outside their original contexts of creation. |
| Specifications, protocols and schemas | Documents | A formal data structure or framework intended to be used as a model.                                                                                                                                         |
| Products                              | Documents | Stable outcomes of creative work.                                                                                                                                                                            |
| Guides                                | Documents | An educational resource or documented protocol meant to instruct readers how to apply relevant tools or techniques.                                                                                          |
| Lists and datasets                    | Documents | A series of consistently organized observations assembled with purpose.                                                                                                                                      |

@@

Perhaps unfortunately then, we also find that nearly 60% of projects have only a single contributor, and projects with more than a dozen are very rare indeed [\<3%].

@@

```{r plot-graph-repo-user}
# TODO
```

>>>>

---
title: "openarchaeoCollaboration"
author:
  - name: Zack Batist
    url: https://zackbatist.github.io
    affiliation: University of Toronto
  - name: Joe Roe
    url: https://joeroe.io
    affiliation: University of Copenhagen
date: "`r Sys.Date()`"
---

@@

| Category                              | Kind      | Scope                                                                                                                                                                                                        |
|:-----------|:-----------|:------------------------------------------------|
| Packages and libraries                | Software  | Sets of functions assembled with clear purpose, and made accessible using standards established by an underlying platform.                                                                                   |
| Standalone software                   | Software  | Software that may be operated without needing to first access an underlying platform.                                                                                                                        |
| Scripts                               | Software  | Sets of pragmatically assembled mutable functions, often lacking complete documentation or adherence to protocols that would otherwise facilitate secondary use outside their original contexts of creation. |
| Specifications, protocols and schemas | Documents | A formal data structure or framework intended to be used as a model.                                                                                                                                         |
| Products                              | Documents | Stable outcomes of creative work.                                                                                                                                                                            |
| Guides                                | Documents | An educational resource or documented protocol meant to instruct readers how to apply relevant tools or techniques.                                                                                          |
| Lists and datasets                    | Documents | A series of consistently organized observations assembled with purpose.                                                                                                                                      |

@@

Perhaps unfortunately then, we also find that nearly 60% of projects have only a single contributor, and projects with more than a dozen are very rare indeed \[\<3%\].

@@

```{r plot-graph-user-user}
# TODO
```
